\section{Future Work}

\paragraph{}
Now that this report is close to answering the initial questions proposed in the beginning there is interest in progressing the research further. With the previously discussed increase in both renewable energy device efficiency and installations of DC systems for data centres and mining sites it would be worth furthering the research in utilising purely DC systems in more applications. 

\paragraph{}
The first suggestion would be to power more devices in small apartment buildings. The suggested layout from experience gained through this research project would be to power constant high loads such as fridges, freezers and air conditioning with the existing AC but all other devices could be powered off DC. To reduce consumption from the grid, renewables can be used for at least partial consumption reduction and a dedicated DC switchboard can be installed for each apartment. 

\paragraph{}
If the system proves successful for small scale homes such as apartments there is cause to see it implemented in areas where reliable electricity is not available. Further analysis into a new supplementary form of micro-grid for essential services such as lighting, cooking and heating should be completed. 

\paragraph{}
***OLD*** 
\newline 
There is still work to be completed on this project before future suggestions on other topics or expansions can be made. The tasks that remain to be completed are outlined in the time line in Section 5. The next major task, as previously discussed, is to use the data provided by QUT as well as floor plans and lighting schematics to model a more feasible design for a commercial building. Once this is completed a more accurate representation of load demand can be analysed. From here specifics of the design can be calculated including current values, voltage drops, cable lengths and locations of devices. Specific devices can be researched and chosen including switchboards, circuit breakers, photovoltaic panels and LED lights. Following calculations and device selection, the financial analysis will be completed as well as an efficiency comparison between a comparable AC system. This is the existing overall plan for completing this project. If hurdles or additional ideas arise throughout, it will be adjusted to allow for the highest quality research possible. 

\newpage